### 2021-01-31 博士/毕业论文/ucasthesis/Tex/Chap_IGCF.tex
完善 IGCF 图片尺寸

\begin{figure} 
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/00893.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/01107.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/01108.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/01564.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/01664.jpg}}\\[0.2ex]
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/01939.jpg}}                     \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/02078.jpg}}                     \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/02285.jpg}}                     \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/02497.jpg}}                     \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/02589.jpg}}\\[0.2ex]
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/02700.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/03000.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/03327.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/03482.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/03733.jpg}}
    \caption{Segmentation results of InstMask on COCO2017 \cite{Lin2014MicrosoftCC} validation dataset.}
    \label{fig:InstMask}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics[width=12cm]{Img/IGCF/instmask1.pdf}
    \caption{Architecture of the tracking framework IGCF.}
    \label{fig:IGCF}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics[width=12cm]{Img/IGCF/net.pdf}
    \caption{Architecture of our InstMask.}
    \label{fig:net}
\end{figure*}

@@

\begin{figure} 
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/birds1/00003.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/birds1/00005.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/birds1/00007.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/birds1/00013.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/birds1/00057.jpg}}\\[0.2ex]
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/book/00002.jpg}}                     \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/book/00005.jpg}}                     \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/book/00011.jpg}}                     \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/book/00013.jpg}}                     \hspace{-0.6em}    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/book/00016.jpg}}\\[0.2ex]
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/butterfly/00015.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/butterfly/00019.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/butterfly/00025.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/butterfly/00027.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/butterfly/00031.jpg}}
    \caption{The tracking result before (green) and after (blue) the instance guided self-correction component.}
    \label{fig:IGSC}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=12cm]{Img/IGCF/vot/eao_rank_vot2015.png}
    \caption{Expected average overlap (EAO) plot on VOT2015 \cite{Kristan2015TheVO}.}
    \label{fig:vot15}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=12cm]{Img/IGCF/vot/eao_rank_vot2016.png}
    \caption{Expected average overlap (EAO) plot on VOT2016 \cite{Kristan2016TheVO}.}
    \label{fig:vot16}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=12cm]{Img/IGCF/got10k/success_plot.png}
    \caption{Overall performance on GOT-10k \cite{Huang2018GOT10kAL}, ranked by their average overlap (AO) scores.}
    \label{fig:got10k}
\end{figure}

@@

\begin{figure} 
    \subfloat{\includegraphics[width=2.43cm]{Img/IGCF/davis16val/paragliding-launch/00001.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.43cm]{Img/IGCF/davis16val/paragliding-launch/00021.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.43cm]{Img/IGCF/davis16val/paragliding-launch/00032.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.43cm]{Img/IGCF/davis16val/paragliding-launch/00069.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.43cm]{Img/IGCF/davis16val/paragliding-launch/00079.jpg}}\\[0.2ex]
    \subfloat{\includegraphics[width=2.43cm]{Img/IGCF/davis16val/parkour/00001.jpg}}                     \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.43cm]{Img/IGCF/davis16val/parkour/00006.jpg}}                     \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.43cm]{Img/IGCF/davis16val/parkour/00026.jpg}}                     \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.43cm]{Img/IGCF/davis16val/parkour/00063.jpg}}                     \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.43cm]{Img/IGCF/davis16val/parkour/00065.jpg}}\\[0.2ex]
    \subfloat{\includegraphics[width=2.43cm]{Img/IGCF/davis16val/bmx-trees/00001.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.43cm]{Img/IGCF/davis16val/bmx-trees/00014.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.43cm]{Img/IGCF/davis16val/bmx-trees/00017.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.43cm]{Img/IGCF/davis16val/bmx-trees/00036.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.43cm]{Img/IGCF/davis16val/bmx-trees/00067.jpg}}
    \caption{Qualitative results of our method in DAVIS2016 VAL dataset.}
    \label{fig:davis}
\end{figure}

>>>>

\begin{figure}
\centering
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/00893.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/01107.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/01108.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/01564.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/01664.jpg}}\\[0.2ex]
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/01939.jpg}}                     \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/02078.jpg}}                     \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/02285.jpg}}                     \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/02497.jpg}}                     \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/02589.jpg}}\\[0.2ex]
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/02700.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/03000.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/03327.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/03482.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.4cm]{Img/IGCF/coco/03733.jpg}}
    \caption{Segmentation results of InstMask on COCO2017 \cite{Lin2014MicrosoftCC} validation dataset.}
    \label{fig:InstMask}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics[width=1.0\textwidth]{Img/IGCF/instmask1.pdf}
    \caption{Architecture of the tracking framework IGCF.}
    \label{fig:IGCF}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics[width=1.0\textwidth]{Img/IGCF/net.pdf}
    \caption{Architecture of our InstMask.}
    \label{fig:net}
\end{figure*}

@@

\begin{figure} 
\centering
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/birds1/00003.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/birds1/00005.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/birds1/00007.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/birds1/00013.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/birds1/00057.jpg}}\\[0.2ex]
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/book/00002.jpg}}                     \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/book/00005.jpg}}                     \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/book/00011.jpg}}                     \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/book/00013.jpg}}                     \hspace{-0.6em}    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/book/00016.jpg}}\\[0.2ex]
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/butterfly/00015.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/butterfly/00019.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/butterfly/00025.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/butterfly/00027.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.45cm]{Img/IGCF/cog/butterfly/00031.jpg}}
    \caption{The tracking result before (green) and after (blue) the instance guided self-correction component.}
    \label{fig:IGSC}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=1.0\textwidth]{Img/IGCF/vot/eao_rank_vot2015.png}
    \caption{Expected average overlap (EAO) plot on VOT2015 \cite{Kristan2015TheVO}.}
    \label{fig:vot15}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=1.0\textwidth]{Img/IGCF/vot/eao_rank_vot2016.png}
    \caption{Expected average overlap (EAO) plot on VOT2016 \cite{Kristan2016TheVO}.}
    \label{fig:vot16}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=1.0\textwidth]{Img/IGCF/got10k/success_plot.png}
    \caption{Overall performance on GOT-10k \cite{Huang2018GOT10kAL}, ranked by their average overlap (AO) scores.}
    \label{fig:got10k}
\end{figure}

@@

\begin{figure}
\centering
    \subfloat{\includegraphics[width=2.43cm]{Img/IGCF/davis16val/paragliding-launch/00001.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.43cm]{Img/IGCF/davis16val/paragliding-launch/00021.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.43cm]{Img/IGCF/davis16val/paragliding-launch/00032.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.43cm]{Img/IGCF/davis16val/paragliding-launch/00069.jpg}}          \hspace{-0.6em}        
    \subfloat{\includegraphics[width=2.43cm]{Img/IGCF/davis16val/paragliding-launch/00079.jpg}}\\[0.2ex]
    \subfloat{\includegraphics[width=2.43cm]{Img/IGCF/davis16val/parkour/00001.jpg}}                     \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.43cm]{Img/IGCF/davis16val/parkour/00006.jpg}}                     \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.43cm]{Img/IGCF/davis16val/parkour/00026.jpg}}                     \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.43cm]{Img/IGCF/davis16val/parkour/00063.jpg}}                     \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.43cm]{Img/IGCF/davis16val/parkour/00065.jpg}}\\[0.2ex]
    \subfloat{\includegraphics[width=2.43cm]{Img/IGCF/davis16val/bmx-trees/00001.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.43cm]{Img/IGCF/davis16val/bmx-trees/00014.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.43cm]{Img/IGCF/davis16val/bmx-trees/00017.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.43cm]{Img/IGCF/davis16val/bmx-trees/00036.jpg}}                   \hspace{-0.6em}
    \subfloat{\includegraphics[width=2.43cm]{Img/IGCF/davis16val/bmx-trees/00067.jpg}}
    \caption{Qualitative results of our method in DAVIS2016 VAL dataset.}
    \label{fig:davis}
\end{figure}
